\bf{Supplementary Material for ``Longitudinal Principal Manifold Estimation"}

### 2025-02-10 manuscript/paper/supplement.tex
restructure paper files

@@

\begin{figure}
    \centering
    \subfloat[\centering Left Hippocampus Volume Estimates]{
      \includegraphics[height=8cm]{adni_plots/adni_lhipp_volume_comp}
      \label{fig:lhipp_volume_comparison}
    }
    \vfill
    \subfloat[\centering Left Thalamus Volume Estimates]{
      \includegraphics[height=8cm]{adni_plots/adni_lthal_volume_comp}
      \label{fig:lthal_volume_comparison}
    }
    \caption{Left hippocampus and left thalamus volume estimates for three ADNI participants. Volume estimates are obtained by summing the volumes of voxels contained within the structure as described by the segmented data (red, circles), LPME (blue, squares), and PME (green, triangles). When PME and LPME are applied to the irregular shape of the hippocampus, there is a clear ordering of the volume estimates. Gaps in the estimated surface induce underestimates of the volume compared to the volume values estimated from the data. These gaps may also cause inconsistency in the LPME volume estimates, resulting in higher aggregate variability than for the data or PME estimates. When applied to the thalamus, the PME-based volume estimates demonstrate similar time point-to-time point changes in the volumes estimated from the segmented data, reflecting the close fit of the PME algorithm to the regularly-shaped thalamus data. The LPME estimates appear to successfully smooth over regions with large variations in subsequent volume measures from the data and PME estimates, as seen for participant 011\_S\_0003.}
\end{figure}

>>>>

\title{\bf{Supplementary Material for ``Longitudinal Principal Manifold Estimation"}}
\author{}

\maketitle

@@

\begin{figure}
    \centering
    \subfloat[\centering Left Hippocampus Volume Estimates]{
      \includegraphics[height=8cm]{adni_plots/adni_lhipp_volume_comp}
      \label{fig:lhipp_volume_comparison}
    }
    \vfill
    \subfloat[\centering Left Thalamus Volume Estimates]{
      \includegraphics[height=8cm]{adni_plots/adni_lthal_volume_comp}
      \label{fig:lthal_volume_comparison}
    }
    \caption{Left hippocampus and left thalamus volume estimates for three ADNI participants. Volume estimates are obtained by summing the volumes of voxels contained within the structure as described by the segmented data (circles, solid line), LPME (squares, dashed line), and PME (triangles, dotted line). When PME and LPME are applied to the irregular shape of the hippocampus, there is a clear ordering of the volume estimates. Gaps in the estimated surface induce underestimates of the volume compared to the volume values estimated from the data. When applied to the thalamus, the PME-based volume estimates demonstrate similar time point-to-time point changes in the volumes estimated from the segmented data, reflecting the close fit of the PME algorithm to the regularly-shaped thalamus data. The LPME estimates appear to successfully smooth over regions with large variations in subsequent volume measures from the data and PME estimates, as seen for participant 033\_S\_0514.}
\end{figure}
